Warming non-randomly speeds up food web fluxes in both an absolute and relative sense

### 2022-04-15 doc/ms/ms.Rmd
updated text. commit before st9 updated.

Warming temperatures are altering biological communities and trophic networks globally. While the influence of warming in food webs is often context-dependent, increasing temperatures are predicted to alter to alter food webs and ecosystems in a couple fundamental ways by 1) decreasing organism body size and 2) increasing metabolic rates. These two attributes, body size and metabolic rate, are important drivers of many ecological patterns. Therefore, warming-induced changes have the potential to propagate through countless ecosystem processes thereby altering the distribution of food webs fluxes, food web stability, and potentially the importance of environmental and biological factors in community assembly. Here, we quantify the patterning and relative distribution of organic matter fluxes through stream food webs spanning a ~25$^\circ$C temperature gradient. We then relate patterns in fluxes to species and community traits (body size, *M* and biomass turnover, *P:B*) within and across ecosystems. We predicted 1) fluxes would skew towards smaller *M* and higher *P:B* both across and within ecosystems and 2) fluxes would be more skewed at higher temperatures. Across the temperature gradient, communities in warmer streams were composed of smaller-bodied and higher-turnover populations on average. Additionally, material fluxes of warmer streams were increasingly skewed towards high-turnover populations *within* the community, showing higher temperatures restructured organic matter fluxes in both an absolute and relative sense. Lastly, in warmer ecosystems the relative distribution of organic matter fluxes appears to be increasingly 'non-random', evidence of potentially stronger selection for these traits with increasing temperature. The emerging picture is a warmer world that is both smaller and faster. Our study lends further support to this pattern and also suggests that

@@

<!--- Connect traits to the 'speed' of ecosystem energy fluxes--->
In fact, reduced organismal body size with warming is considered a 'universal' response to climate change [@atkinson1994; @gardner2011; @daufresne2009]. Body size reductions arise from multiple mechanisms acting at different levels of organization, such as the increased relative abundance of smaller species within warmer communities [@bergmann1848], or smaller individuals in warmer populations [@james1970], or through reduced body size of warmer individuals [@atkinson1994]. Temperature-size relationships (TSR) are likely to influence the distribution of body sizes both across and within ecosystems, such that warmer communities should contain smaller species and populations, on average, and smaller organisms should be more dominant within a community. These changes can have important implications for ecosystems pattern and processes because body size is a strong determinant of an organism's biology [@peters1983] influencing, life history [@zeuss2017; @altermatt2010; @nelson2020b], development [@angilletta2004], and crucially, basal metabolic rate [@brown2004; @gillooly2001].

<!--- Write the main goals of the paragraph--->
Organismal metabolic rate, in addition to being controlled by body size, is strongly influenced by temperature [@gillooly2001]. Therefore, temperature may alter metabolic rate indirectly through reductions in body size, as well as directly through its effects on subcellular kinetics [@bideault2019; @osmond2017]. The interactive effect of these processes has been shown to modulate ecosystem patterns through effects on population abundance [@bernhardt2018], consumer-resource interactions [@bideault2019], and food web structure [@gibert2019a]. Importantly, the kinetic effects of temperatures are tied to many biological processes [@dell2014], among them growth rate [@gillooly2001], developmental rate [@zuo2012; @nelson2020b], voltinism [@zeuss2017], and population turnover rate [@huryn2007; @brown2004]. As such, the emerging picture suggests a smaller, faster world in which warming "speeds up" ecosystem processes through the compounded effects of smaller body size and higher turnover rates.

@@

Macroinvertebrate diets were quantified for dominant taxa in each stream. We focused on numerically abundant taxa and/or taxa with relatively
high annual production. A minimum of five individuals were selected from samples, and, when possible included individuals of different size classes to account for ontogenetic
shifts in diet. We included individuals from different seasons to capture concurrent ontogenetic and seasonal changes. For small-bodied taxa, we combined multiple individuals (*n*
= 3--5) to ensure samples contained enough material for quantification. We used methods outlined in Rosi-Marshall [-@rosi-marshall2016] to remove gut tracts and prepare gut contents for quantification. Briefly, we removed the foregut from each individual or collection of individuals and sonicated contents in water for 30 seconds. Gut content slurries were filtered
onto gridded nitrocellulose membrane filters (Metricel GN-6, 25 mm, 0.45 $\mu$m pore size; Gelman Sciences, Ann Arbor, MI, USA), dried at 60 $^\circ$C for 15 min, placed on a
microscope slide, cleared with Type B immersion oil, and covered with a cover slip. We took 5--10 random photographs under 200--400x magnification, depending on the density of
particles, using a digital camera mounted on a compound microscope. From these photographs we identified all particles within each field and measured the relative area of particles
using image analysis software [@schindelin2012]. We classified particles into six categories: diatoms, green and filamentous algae, cyanobacteria, amorphous detritus, vascular and non-vascular
plants (e.g., bryophytes), and animal material. We calculated the proportion of each food category in the gut by dividing their summed area by the total area of all particles. Gut
contents of many predators were empty or contained unidentifiable, macerated prey. For these taxa, we assumed 100% animal material.

@@

Patterns of OM flux among streams were most closely tied to total consumer energy demands as consumer diets exhibited high similarity among streams (Supporting Materials, Figure S1). Diets composition among all streams were dominated by diatoms (`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`]), amorphous detritus (`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`]), and green algae (`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`]). Within streams, diet similarity ranged from `r min_within_overlap %>% dplyr::select(meanoverlap_mean) %>% round(2)` (`r round(min_within_overlap$meanoverlap_quant2.5,2)` -- `r round(min_within_overlap$meanoverlap_quant97.5,2)`) to `r max_within_overlap %>% dplyr::select(meanoverlap_mean) %>% round(2)` (`r round(max_within_overlap$meanoverlap_quant2.5,2)` -- `r round(max_within_overlap$meanoverlap_quant97.5,2)`) among all consumer taxa. Among streams, diet overlap was similarly high and mean overlap among all streams was `r round(among_overlap_mean,2)`% (`r round(among_overlap_quant2.5,2)` -- `r round(among_overlap_quant97.5,2)` 95% PI). Diet similarity of pairwise comparisons among streams showed little differences in diet among streams and no clear relationship with temperature.

Generally, organic matter fluxes were dominated by insect species from *Simuliidae* and *Chironomidae* families (Figure 1a). In warmer streams, OM fluxes shifted toward the pulmonate snail, *Radix balthica*. In the warmest stream, where maximum temperatures approach ~40$^\circ$C, OM fluxes were dominated by worms of family *Naididae*, the midge *Cricotpous sylvestris*, and *Radix balthica*.

```{r figure 1, echo = FALSE, warning = FALSE, message = FALSE, fig.width=7.5, fig.height=6, dpi = 450, fig.cap="Figure 1. Patterns of OM flux among populations based on (a) Rank ordering of annual population organic matter flux log~e~(mg m^-2^ y^-1^) and (b) relative OM flux among taxaonomic groups in consumer communities and across the temperature gradient."}
drake::loadd(annual_spp_flux_fig)
drake::loadd(spp_flux_dist)
gridExtra::grid.arrange( spp_flux_dist,annual_spp_flux_fig, ncol = 2, layout_matrix = cbind(1,1,1,1,2,2,2))
```

@@

Organic matter fluxes were distributed unevenly among consumers, however, the extent varied among streams (Figure 1b; Figure S1). Gini inequality coefficients ranged from `r gini_summary %>% select('Non.normalized.Gini_mean') %>% min %>% round(2)` (`r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>% select(Non.normalized.Gini_quant2.5) %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_quant97.5') %>% round(2)`) to `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_mean') %>% round(2)` (`r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant2.5') %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant97.5') %>% round(2)`; Table 1). Differences in inequality were partly attributed to variation in consumer species richness among streams which ranged from `r spp_richness %>% select(taxon_n) %>% min` to `r spp_richness %>% select(taxon_n) %>% max` consumer groups. Yet, even after accounting for differences in consumer richness, patterns of material fluxes were still unevenly distributed among consumers (Normalized Gini coefficient: `r gini_summary %>% select('Normalized.Gini_mean') %>% min %>% round(2)` (`r gini_summary %>% data.frame %>% dplyr::slice_min(Normalized.Gini_mean) %>% select(Normalized.Gini_quant2.5) %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_min(Normalized.Gini_mean) %>%  select('Normalized.Gini_quant97.5') %>% round(2)`) to `r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>%  select('Normalized.Gini_mean') %>% round(2)` (`r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>% select('Normalized.Gini_quant2.5') %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>% select('Normalized.Gini_quant97.5') %>% round(2)`; Table 1).

@@

Variation in the relative distribution of OM fluxes among consumers corresponded to different patterns of dominance across streams (Figure 1b). For example, in an absolute sense, ~85% of total flux was contributed by `r n_dom_min$n_dom` to `r n_dom_max$n_dom` species. Relatively, this flux was attributed by `r round(perc_dom_min$dom_spp*100,0)`% to `r round(perc_dom_max$dom_spp*100,0)`% of the species assemblages within streams. Differences in dominance were unrelated to temperature, however, species dominance in relation to population traits exhibited important differences along the temperature gradient.

@@

Warmer streams had communities with smaller mean body sizes and faster turnover rates on average (Figure 2).   
The fluxes of OM were distributed differently across body sizes and turnover rates (*P:B*) among and within streams. Across streams, mean body size of taxa ranged from `r m_summ %>% slice_min(M_mg_ind_mean) %>% select(M_mg_ind_mean) %>% round(2)` to `r m_summ %>% slice_max(M_mg_ind_mean) %>% select(M_mg_ind_mean)%>% round(2)` mg ind^-1^ and mean annual P:B ranged from `r pb_summ %>% slice_min(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` to `r pb_summ %>% slice_max(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` (Figure 2). Both, *M* and *P:B* showed associations with mean annual stream temperature that were negative and positive, respectively. Generally, mean *M* of the community decreased `r M_temp_coef_mean`% (95% PI, `r M_temp_coef_quant2.5`% -- `r M_temp_coef_quant97.5`%) for each increase in 1$^\circ$C. In contrast, mean population *P:B* of the community increased `r pb_temp_coef_mean`% (95% PI, `r pb_temp_coef_quant2.5`% -- `r pb_temp_coef_quant97.5`%) for each 1$^\circ$C in mean annual stream temperature. Material fluxes within consumer communities were skewed towards larger body sizes (positive skew), towards smaller body sizes (negative skew), or neutrally in regards to body size  among streams, with skew estimates with body size (*M*) ranging from `r m_skew_summ %>% slice_min(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` to `r m_skew_summ %>% slice_max(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean) %>% round(2)` (Figure 3, Table 2). Similarly, skew in fluxes towards high turnover taxa varied among streams ranging from `r pb_skew_summ %>% slice_min(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` to `r pb_skew_summ %>% slice_max(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` (Figure 3, Table 2).

Across communities, average population body size, *M*, decreased and average biomass turnover, *P:B*, increased with increasing temperature (Figure 1). Mean population *M* decreased from `r ann_spp_summ %>% dplyr::select(M_mg_ind_mean) %>% max %>% round(2)` (`r ann_spp_summ %>% dplyr::slice_max(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_max(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant97.5) %>% round(2)`) in the coldest stream to `r ann_spp_summ %>% dplyr::select(M_mg_ind_mean) %>% min %>% round(2)` (`r ann_spp_summ %>% dplyr::slice_min(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_min(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant97.5) %>% round(2)`) in the warmest stream. This decrease corresponded to a `r (exp(mean(m_spp_temp_coefs, na.rm = TRUE)) - 1)*100 %>% round(2)` (`r (exp(quantile(m_spp_temp_coefs,0.025, na.rm = TRUE)) - 1)*100 %>% round(2)`--`r (exp(quantile(m_spp_temp_coefs,0.975, na.rm = TRUE)) - 1)*100 %>% round(2)`) percent decrease in mean population body size (mg ind^-1^) for every increase of 1$^\circ$C. In contrast, the average population *P:B* increased from `r ann_spp_summ %>% dplyr::select(pb_y_mean) %>% max %>% round(2)` (`r ann_spp_summ %>% dplyr::slice_max(pb_y_mean) %>% dplyr::select(pb_y_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_max(pb_y_mean) %>% dplyr::select(pb_y_quant97.5) %>% round(2)`) in the coldest stream to `r ann_spp_summ %>% dplyr::select(pb_y_mean) %>% min %>% round(2)` (`r ann_spp_summ %>% dplyr::slice_min(pb_y_mean) %>% dplyr::select(pb_y_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_min(pb_y_mean) %>% dplyr::select(M_mg_ind_quant97.5) %>% round(2)`) in the warmest stream. This increase corresponded to a `r (exp(mean(pb_spp_temp_coefs, na.rm = TRUE)) - 1)*100 %>% round(2)` (`r (exp(quantile(pb_spp_temp_coefs,0.025, na.rm = TRUE)) - 1)*100 %>% round(2)`--`r (exp(quantile(pb_spp_temp_coefs,0.975, na.rm = TRUE)) - 1)*100 %>% round(2)`) percent decrease in mean population body size (mg ind^-1^) for every increase of 1$^\circ$C (Figure 1).

The skew of OM fluxes towards populations with smaller/larger body sizes showed a small, yet systematic association with stream temperature (Figure 4). The median effect size of increasing temperature was to shift the skewness coefficient, $Sk_{flux}$, `r M_skew_temp_coef_median` units (`r M_skew_temp_coef_quant2.5`--`r M_skew_temp_coef_quant97.5` 95% PI) for every 1$^\circ$C increase. Similarly, OM fluxes through the community skewed increasingly toward higher turnover (*P:B*) organisms with increasing temperature. The median increase in $Sk_{flux}$ towards higher *P:B* populations was `r pb_skew_temp_coef_mean` (`r pb_skew_temp_coef_quant2.5`--`r pb_skew_temp_coef_quant97.5` 95% PI; Figure 4).

```{r lorenz analysis, echo =FALSE, warning=FALSE, message=FALSE, fig.width=3.5, fig.height=5, dpi = 450, fig.cap="Figure 3. Lorenz curves of cumulative relative organic matter flux with increasing cumulative species. Species are ranked along trait axis of (a) mean body size (mg^-ind^) and (b) population turnover (production:biomass ratio, *P:B*, y^-1^), such that x~1~ < x~2~ < x~i~ <...x~S~, where x is the trait value of species *i*."}

@@

For example, we lack a complete understanding of TSRs to explain deviations that exist across taxonomic groups (e.g., diatoms, @adams2013; invertebrates @zeuss2017; birds @geist1987; and fish @rypel2014). Explanations for these deviations vary [@ohlberger2013], some highlight additional processes such as competition and predation [@delong2014], while others propose alternative models of organism body size optimization, such as the balance of resource supply and energy demand [e.g., @kozlowski2004; @delong2012a]. Crucially, these alternative models highlight the trade-off between asymptotic body size and metabolic demand [@delong2012a] that can shape life history patterns (i.e., voltinism, @zeuss2017; @nelson2020b).  and community structure across ecosystems...*better transition here. Trying to get into P:B and why it should be selected*

@@

>>>>

Warming temperatures are altering communities and trophic networks globally. While the influence of warming in food webs is often context-dependent, increasing temperatures are predicted to alter to alter food webs and ecosystems in a couple general and fundamental ways: 1) decreasing organism body size and 2) increasing metabolic rates. Both body size and metabolic rate are important drivers of many ecological patterns. Therefore, warming-induced changes have the potential to propagate through countless ecosystem processes thereby altering the distribution of food webs fluxes, food web stability, and potentially the importance of environmental and biological factors in community assembly. Here, we quantify the patterning and relative distribution of organic matter fluxes through stream food webs spanning a natural ~25$^\circ$C temperature gradient. We then related patterns in fluxes to species and community traits (body size, *M* and biomass turnover, *P:B*) within and across ecosystems. We predicted 1) fluxes would skew towards smaller *M* and higher *P:B* both across and within ecosystems and 2) fluxes would be more skewed at higher temperatures. Across the temperature gradient, communities in warmer streams were composed of smaller-bodied and higher-turnover populations on average. Additionally, material fluxes of warmer streams were increasingly skewed towards high-turnover populations *within* the community, showing higher temperatures restructured organic matter fluxes in both an absolute and relative sense. Lastly, in warmer ecosystems the relative distribution of organic matter fluxes appears to be increasingly 'non-random', evidence of potentially stronger selection for these traits with increasing temperature. The emerging picture is a warmer world that is both smaller and faster. Our study lends further support to this pattern and suggests that temperature will become an increasingly important environmental filter on warming communities in the future.
\newpage

@@

<!--- Connect traits to the 'speed' of ecosystem energy fluxes--->
In fact, reduced organismal body size with warming is considered a 'universal' response to climate change [@atkinson1994; @gardner2011; @daufresne2009]. Body size reductions arise from multiple mechanisms acting at different levels of organization, such as the increased relative abundance of smaller species within warmer communities [@bergmann1848], or smaller individuals in warmer populations [@james1970], or through reduced body size of warmer individuals [@atkinson1994]. Temperature-size relationships (TSR) are likely to influence the distribution of body sizes both across and within ecosystems, such that warmer communities should contain smaller species and populations, on average, and smaller organisms should be more dominant within a community. These changes can have important implications for ecosystems pattern and processes because body size is a strong determinant of an organism's biology [@peters1983] influencing, life history patterns [@zeuss2017; @altermatt2010; @nelson2020b], and developmental [@angilletta2004] and metabolic rates [@brown2004; @gillooly2001].

<!--- Write the main goals of the paragraph--->
Organismal metabolic rate, in addition to being controlled by body size, is strongly influenced by temperature [@gillooly2001]. Therefore, temperature may alter metabolic rate indirectly through reductions in body size, as well as directly through its effects on subcellular kinetics [@bideault2019; @osmond2017]. The interactive effect of these processes has been shown to modulate ecosystem patterns through effects on population abundance [@bernhardt2018], consumer-resource interactions [@bideault2019], and food web structure [@gibert2019a]. Importantly, the kinetic effects of temperatures are tied to many biological processes [@dell2014], among them growth rate [@gillooly2001], developmental rate [@zuo2012; @nelson2020b], voltinism [@zeuss2017], and population turnover rate [@huryn2007; @brown2004]. As such, the emerging picture suggests a smaller, faster world in which warming "speeds up" ecosystem processes through the compounded effects of smaller body size and higher turnover rates.*possibly simplify the paragraph and combined with above*

@@

Macroinvertebrate diets were quantified for dominant taxa in each stream. We focused on numerically abundant taxa and/or taxa with relatively
high annual production. A minimum of five individuals were selected from samples, and, when possible included individuals of different size classes to account for ontogenetic
shifts in diet. We included individuals from different seasons to capture concurrent ontogenetic and seasonal changes. For small-bodied taxa, we combined multiple individuals (*n*
= 3--5) to ensure samples contained enough material for quantification. We used methods outlined in Rosi-Marshall [-@rosi-marshall2016] to remove gut tracts and prepare gut contents for quantification. Briefly, we removed the foregut from each individual or collection of individuals and sonicated contents in water for 30 seconds. Gut content slurries were filtered
onto gridded nitrocellulose membrane filters (Metricel GN-6, 25 mm, 0.45 $\mu$m pore size; Gelman Sciences, Ann Arbor, MI, USA), dried at 60 $^\circ$C for 15 min, placed on a
microscope slide, cleared with Type B immersion oil, and covered with a cover slip. We took 5--10 random photographs under 200--400x magnification, depending on the density of
particles, using a digital camera mounted on a compound microscope. From these photographs we identified all particles within each field and measured the relative area of particles
using image analysis software [@schindelin2012]. We classified particles into six categories: diatoms, green and filamentous algae, cyanobacteria, amorphous detritus, vascular and non-vascular
plants (e.g., bryophytes), and animal material and then calculated the proportion of each food category in the gut by dividing their summed area by the total area of all particles. Gut
contents of many predators were empty or contained unidentifiable, macerated prey. For these taxa, we assumed 100% animal material.

@@

Patterns of OM flux among streams were most closely tied to total consumer energy demands as consumer diets exhibited high similarity among streams (Supporting Materials, Figure S1). Diets composition among all streams were dominated by diatoms (`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`%; `r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)` 95% PI), amorphous detritus (`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`%;`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)` 95% PI), and green algae (`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`%;`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)` 95% PI). Within streams, diet similarity ranged from `r min_within_overlap %>% dplyr::select(meanoverlap_mean) %>% round(2)` (`r round(min_within_overlap$meanoverlap_quant2.5,2)` -- `r round(min_within_overlap$meanoverlap_quant97.5,2)`) to `r max_within_overlap %>% dplyr::select(meanoverlap_mean) %>% round(2)` (`r round(max_within_overlap$meanoverlap_quant2.5,2)` -- `r round(max_within_overlap$meanoverlap_quant97.5,2)`) among all consumer taxa. Among streams, diet overlap was similarly high and mean overlap among all streams was `r round(among_overlap_mean,2)`% (`r round(among_overlap_quant2.5,2)` -- `r round(among_overlap_quant97.5,2)` 95% PI). Diet similarity of pairwise comparisons among streams showed little differences in diet among streams and no clear relationship with temperature.

@@

@@

Generally, organic matter fluxes were dominated by insect species from Simuliidae and Chironomidae families (Figure 1a) and were distributed unevenly (Figure 1b; Figure S1). In an absolute sense, ~85% of total flux was contributed by between `r n_dom_min$n_dom` and `r n_dom_max$n_dom` consumer groups. Relatively, this flux was attributed by `r round(perc_dom_min$dom_spp*100,0)`% to `r round(perc_dom_max$dom_spp*100,0)`% of the consumer assemblage within streams. Differences in inequality were partly attributed to variation in consumer species richness among streams which ranged from `r spp_richness %>% select(taxon_n) %>% min` to `r spp_richness %>% select(taxon_n) %>% max` consumer groups. Gini inequality coefficients ranged from `r gini_summary %>% select('Non.normalized.Gini_mean') %>% min %>% round(2)` (`r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>% select(Non.normalized.Gini_quant2.5) %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_quant97.5') %>% round(2)` 95% PI) to `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_mean') %>% round(2)` (`r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant2.5') %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant97.5') %>% round(2)` 95% PI; Table 1). In warmer streams, OM fluxes shifted toward the black fly, *Simuliium vittatum* and the pulmonate snail, *Radix balthica*. In the warmest stream, where maximum temperatures approach ~40$^\circ$C, species richness was lowest and OM fluxes were dominated by oligochaete worms of family Naididae, the chironomid *Cricotpous sylvestris*, and *Radix balthica*. Yet, even after accounting for differences in consumer richness, patterns of material flux were still unevenly distributed among consumers (Normalized Gini coefficient: `r gini_summary %>% select('Normalized.Gini_mean') %>% min %>% round(2)` (`r gini_summary %>% data.frame %>% dplyr::slice_min(Normalized.Gini_mean) %>% select(Normalized.Gini_quant2.5) %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_min(Normalized.Gini_mean) %>%  select('Normalized.Gini_quant97.5') %>% round(2)` 95% PI) to `r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>%  select('Normalized.Gini_mean') %>% round(2)` (`r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>% select('Normalized.Gini_quant2.5') %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>% select('Normalized.Gini_quant97.5') %>% round(2)` 95% PI; Table 1). Differences in evenness and dominance were unrelated to temperature, however, species dominance in relation to population traits exhibited important differences along the temperature gradient.

```{r figure 1, echo = FALSE, warning = FALSE, message = FALSE, fig.width=7.5, fig.height=6, dpi = 450, fig.cap="Figure 1. Patterns of OM flux among populations based on (a) relative OM flux among taxonomic groups in consumer communities and descending the temperature gradient from the warmest (27.2$^\\circ$C) on top pane to coldest (5.0$^\\circ$C) on the botthom. (b) The rank ordering of annual population organic matter flux log~e~(mg m^-2^ y^-1^) of consumer groups. In (a), consumer groups fill is based on taxonomic family and the full key of consumer group abbreviations can be found in supporting materials."}

drake::loadd(annual_spp_flux_fig)
drake::loadd(spp_flux_dist)
gridExtra::grid.arrange( spp_flux_dist,annual_spp_flux_fig, ncol = 2, layout_matrix = cbind(1,1,1,1,2,2,2))
```

@@

Across communities, average population body size, *M*, decreased and average biomass turnover, *P:B*, increased with increasing temperature (Figure 2). Mean population *M* decreased from `r ann_spp_summ %>% dplyr::select(M_mg_ind_mean) %>% max %>% round(2)` (`r ann_spp_summ %>% dplyr::slice_max(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_max(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant97.5) %>% round(2)` 95% PI) in the coldest stream to `r ann_spp_summ %>% dplyr::select(M_mg_ind_mean) %>% min %>% round(2)` (`r ann_spp_summ %>% dplyr::slice_min(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_min(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant97.5) %>% round(2)` 95% PI) in the warmest stream. This decrease corresponded to a `r ((exp(mean(m_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(2)` (`r ((exp(quantile(m_spp_temp_coefs,0.025, na.rm = TRUE)) - 1)*100) %>% round(2)`--`r ((exp(quantile(m_spp_temp_coefs,0.975, na.rm = TRUE)) - 1)*100) %>% round(2)` 95% PI) percent decrease in mean population body size (mg ind^-1^) for every increase of 1$^\circ$C. In contrast, the average population *P:B* increased from `r ann_spp_summ %>% dplyr::select(pb_y_mean) %>% max %>% round(2)` (`r ann_spp_summ %>% dplyr::slice_max(pb_y_mean) %>% dplyr::select(pb_y_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_max(pb_y_mean) %>% dplyr::select(pb_y_quant97.5) %>% round(2)` 95% PI) in the coldest stream to `r ann_spp_summ %>% dplyr::select(pb_y_mean) %>% min %>% round(2)` (`r ann_spp_summ %>% dplyr::slice_min(pb_y_mean) %>% dplyr::select(pb_y_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_min(pb_y_mean) %>% dplyr::select(M_mg_ind_quant97.5) %>% round(2)` 95% PI) in the warmest stream. This increase corresponded to a `r ((exp(mean(pb_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(2)` (`r ((exp(quantile(pb_spp_temp_coefs,0.025, na.rm = TRUE)) - 1)*100) %>% round(2)`--`r ((exp(quantile(pb_spp_temp_coefs,0.975, na.rm = TRUE)) - 1)*100) %>% round(2)` 95% PI) percent decrease in mean population body size (mg ind^-1^) for every increase of 1$^\circ$C (Figure 2).

Organic matter fluxes within consumer communities were skewed towards larger body sizes (positive skew), towards smaller body sizes (negative skew), or neutrally in regards to body size among streams. Skew estimates with body size (*M*) ranging from `r m_skew_summ %>% slice_min(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` to `r m_skew_summ %>% slice_max(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean) %>% round(2)` (Figure 3, Table 2). Similarly, skew in fluxes towards high *P:B* taxa varied among streams ranging from `r pb_skew_summ %>% slice_min(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` to `r pb_skew_summ %>% slice_max(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` (Figure 3, Table 2). The skew of OM fluxes towards populations with smaller/larger body sizes showed a small, yet systematic association with stream temperature (Figure 4a). The median effect size of increasing temperature was to shift the skewness coefficient, $Sk_{flux}$, `r M_skew_temp_coef_median` units (`r M_skew_temp_coef_quant2.5`--`r M_skew_temp_coef_quant97.5` 95% PI) for every 1$^\circ$C increase. Similarly, OM fluxes through the community skewed increasingly toward higher turnover (*P:B*) organisms with increasing temperature. The median increase in $Sk_{flux}$ towards higher *P:B* populations was `r pb_skew_temp_coef_mean` (`r pb_skew_temp_coef_quant2.5`--`r pb_skew_temp_coef_quant97.5` 95% PI; Figure 4c).

```{r lorenz analysis, echo =FALSE, warning=FALSE, message=FALSE, fig.width=4.0, fig.height=7, dpi = 450, fig.cap="Figure 3. Lorenz curves of cumulative relative organic matter flux with increasing cumulative species. Species are ranked along trait axis of (a) mean body size (mg ind^-1^) and (b) population turnover (production:biomass ratio, *P:B*, y^-1^), such that x~1~ < x~2~ < x~i~ <...x~S~, where x is the trait value of species *i*."}

@@

@@

Spare(d) words
